Variability as a better characterization of Shannon entropy

### 2021-01-15 Articles/2019-ShannonEntropy/Submissions/EJP/response.tex

\emph{	When considering continuous distributions, we have to remember that the densities are given per unit. [...] A distribution over half a unit interval will correspond to minus one bit, since we would need to ``lose'' one bit of information to widen the variability back to one unit. In other words, the variability is measured by the number of bits needed to identify an element up to one unit.}

Given the complete mischaracterization of the prose and the erroneous claim that somehow the choice of unit/granularity makes the Shannon entropy always positive, we find it impossible to understand whether there is any meaningful item to address. One possible answer is that the referreee does not realize that choosing a unit, in the context of information entropy, is equivalent to choosing the resolution since it changes the zero for entropy... The $\Delta$ \textbf{is} the unit. We added the words ``granularity'' and ``resolution'' in a few places where units are discussed.

\begin{quote}
Actually, the authors clearly show their general lack of understanding of the importance of granularity in entropy considerations (especially entropy essentially being a scale-less quantity) since they consider the Shannon entropy to be somehow ‘perplexing’ since it changes when the scale is stretched, shrunk, or changed. However, this is simply equivalent to a change of granularity (or scale) where it is well known that the calculated entropy will therefore always concomitantly change. 
\end{quote}
Again, it is difficult to understand whether, hidden under the personal attacks, there is an actual point. The word `perplexing' was used in the following paragraph:

@@

\emph{	This should be particularly perplexing if we want to use this quantity in a physical setting. If we want $\rho(x)$ to represent the state of a macroscopic system and $H(\rho(x))$ to represent entropy, a state variable, how can $H$ change value if we merely express $\rho$ over different coordinates? How can maximization of entropy be meaningful if it yields different results depending on the coordinate system? Does that mean that we can use the Shannon formula only on distributions over discrete values?}

The word `perplexing' is used as a rhetorical device, to introduce questions a newcomer might find puzzling, which we answer in the following paragraph. Does the referee really think that means we find the issue perplexing? This would leave us very perplexed...

We modified the first sentence to read:

\emph{This may seem particularly perplexing given that we want to use this quantity in a physical setting.}

@@

\begin{quote}
The authors comment that “infinitesimally narrow distributions, like delta functions, do not work well with the Shannon [entropy]”. It is well known that delta functions always require extreme care in their handling, since they are intrinsically unphysical (not conforming to many of the key requirements of physically plausible functions, such as causality and the absence of infinities etc.); so to suggest that the Shannon entropy is somehow inappropriate due to its having apparent problems with the delta function is fatuous – it just means that the delta function is not being appropriately applied. 
\end{quote}
Again, if the referee actually read what we wrote, he would have seen that we say exactly the same thing: that one has to work with functions that have small but still finite support.

\begin{quote}
The authors make a curious comment about the Boltzmann constant, that it “is really just set by the unit system”, as if it isn’t a universal constant and is simply a matter of convention! 
\end{quote}
In the last revision of the SI, universal constants \textbf{are} set to selected values, no longer measured: they are a matter of convention. They are called \textbf{defining constants} because they define the unit system, which is a convention. Before engaging in comments that imply we are incompetent, the referee may want to read the relevant literature, which is now included in the paper.

@@

We added the following footnotes, merely as a pointer for the curious reader:

\emph{In the latest revision of the International Metric System of Units SI, the Boltzmann constant is one of the defining constants. This means its value is assigned, rather than measured, in a way that properly defines Kelvin, the unit of temperature. The universal constants are essentially used as fixed starting points to define our measurement scales.}

### 2021-01-15 Articles/2019-ShannonEntropy/Submissions/EJP/EJP-ShannonEntropyIsVariability.tex
Incorporating feedback from Julian

This should be particularly perplexing if we want to use this quantity in a physical setting. If we want $\rho(x)$ to represent the state of a macroscopic system and $H(\rho(x))$ to represent entropy, a state variable, how can $H$ change value if we merely express $\rho$ over different coordinates? How can maximization of entropy be meaningful if it yields different results depending on the coordinate system? Does that mean that we can use the Shannon formula only on distributions over discrete values?

@@

The Boltzmann constant $k_B$ should not distract us: its role is simply to allow us to measure temperature in an appropriate unit.\footnote{In the latest revision of the International Metric System of Units SI,\cite{chyla2011evolution} the Boltzmann constant is one of the defining constants. This means its value is assigned, rather then measured, in a way that properly defines Kelvin, the unit of temperature. The universal constants are essentially used as fixed starting points to define our measurement scales.
}
If one defines $T = \frac{\partial U}{\partial S}$, and measures temperature in Kelvin and energy in Joules, the above relationship forces us to measure entropy in Joules/Kelvin. Therefore the entropy cannot be expressed as a pure number. However, this is not the only possible definition. Instead of using $T$ as a primary thermodynamic variable, we can use $\beta = \frac{1}{k_B T}$. In this case, one would define $\beta = \frac{\partial S}{\partial U}$, measure energy in Joules, $\beta$ in inverse Joules and entropy would be dimensionless. As one can do all the thermodynamic calculations using just $\beta$, the constant $k_B$ is really just set by the unit system.\footnote{As \cite{chyla2011evolution} notes:
\begin{quote}
	Temperature characterizes the average thermal energy of particles in a certain ensemble of particles in the state of thermodynamic equilibrium. Therefore, in principle, one could express this quantity in terms of the unit of energy; this is actually practiced in many fields of physics, especially in statistical physics, where it is quite common to use $\Theta = k_B T$ or $\beta = 1 / k_B T$  as a measure of thermal energy, instead of temperature $T$ measured in Kelvins.
\end{quote}
}

>>>>

This may seem particularly perplexing given that we want to use this quantity in a physical setting. If we want $\rho(x)$ to represent the state of a macroscopic system and $H(\rho(x))$ to represent entropy, a state variable, how can $H$ change value if we merely express $\rho$ over different coordinates? How can maximization of entropy be meaningful if it yields different results depending on the coordinate system? Does that mean that we can use the Shannon formula only on distributions over discrete values?

@@

The Boltzmann constant $k_B$ should not distract us: its role is simply to allow us to measure temperature in an appropriate unit.\footnote{In the latest revision of the International Metric System of Units SI,\cite{chyla2011evolution} the Boltzmann constant is one of the defining constants. This means its value is assigned, rather than measured, in a way that properly defines Kelvin, the unit of temperature. The universal constants are essentially used as fixed starting points to define our measurement scales.
}
If one defines $T = \frac{\partial U}{\partial S}$, and measures temperature in Kelvin and energy in Joules, the above relationship forces us to measure entropy in Joules/Kelvin. Therefore the entropy cannot be expressed as a pure number. However, this is not the only possible definition. Instead of using $T$ as a primary thermodynamic variable, we can use $\beta = \frac{1}{k_B T}$. In this case, one would define $\beta = \frac{\partial S}{\partial U}$, measure energy in Joules, $\beta$ in inverse Joules and entropy would be dimensionless. As one can do all the thermodynamic calculations using just $\beta$, the constant $k_B$ is really just set by the unit system.\footnote{As \cite{chyla2011evolution} notes:
\begin{quote}
	Temperature characterizes the average thermal energy of particles in a certain ensemble of particles in the state of thermodynamic equilibrium. Therefore, in principle, one could express this quantity in terms of the unit of energy; this is actually practiced in many fields of physics, especially in statistical physics, where it is quite common to use $\Theta = k_B T$ or $\beta = 1 / k_B T$  as a measure of thermal energy, instead of temperature $T$ measured in Kelvins.
\end{quote}
}
